%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry{Senior Developer}
{101 Ways}
{Amsterdam, Netherlands - Hybrid}
{Nov 2023 - Jan 2024}
{I was brought in to help the teams build the 2nd version of their service and migrate to it.}
\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
\xdef\tpd{\the\prevdepth}
\begin{cventrystack}
	\cventry
	{Senior Developer} % Job title
	{Recharge} % Organization
	{}
	{}
	{
		\begin{cvitems}
			\item {I developed the AWS infrastructure in Typescript with CDKTF}
			\item {Automated storybook for PR environments}
			\item {Implemented the first Database storage for the new version}
			\item {Automated external docker images storage}
			\item {Implemented the first Cloudfront distribution for the new version}
			\item {Collaborated on the AWS EKS setup}
			\item {Built CI/CD pipelines with Github Actions}
			\item {Provided guidance on architecture decissions}
			\item {\bfseries{Technologies:} AWS, Typescript, CDKTF, Kubernetes, Istio, Github Actions, BASH}
		\end{cvitems}
	}
\end{cventrystack}
\end{minipage}

\cventry
{Freelance DevOps Engineer} % Job title
{DPG Media} % Organization
{Amsterdam, Netherlands - Hybrid} % Location
{Jun 2023 - Oct 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
I was brought in to containerize and migrate the subscription applications of DPG from EC2 to ECS.
\newline \hfill
	\begin{cvitems}
		\item {Architected the Landing Zone - with best practises - for the ECS setup}
		\item {Developed a Terraform module to easily replicate \emph{non-prod} and \emph{prod} environments}
		\item {Developed a custom deployment pipe to enable deployments on the new environments - Python}
		\item {Setup monitoring and log streaming into OpenSeach}
		\item {Automated AWS infrastructure cost control - Lambdas}
		\item {Developed a scalable setup for segragated test environments - each dev own test enviroment}
		\item {Delivered documentation for the new setup}
		\item {\bfseries{Technologies:} AWS, Terraform, Docker, Python, Bash, BitBucket pipelines}
	\end{cvitems}
}

\cventry{Freelance Cloud Engineer}
{ZEN Software}
{Alkmaar, Netherlands - Hybrid}
{Mar 2022 - Dec 2022}
{I was brought in to migrate the build, test and deployment of a monolithic Java application in the cloud.}
\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
\xdef\tpd{\the\prevdepth}
\begin{cventrystack}
	\cventry
	{Cloud Solution Engineer} % Job title
	{Maxeda} % Organization
	{}
	{}
	{
		\begin{cvitems}
			\item {Designed and implemented a new CI/CD pipeline stack for a Java based backend app}
			\item {Automated manual CI/CD pipelines into BitBucket cloud}
			\item {Brought self-hosted BitBucket runners for critical pipelines}
			\item {Hacked BitBucket self-hosted runners to use buildkit and full caching mechanism}
			\item {Built infrastructure with Terraform on AWS}
			\item {Implemented docker-compose setup for local application development}
			\item {Developed a Terraform module to migrate from Ansible}
			\item {Developed a lambda based mechanism to dynamically toggle AWS WAF challenge}
			\item {Implemented an environmentally friendly script to prevent overlapping pipeline runs - fun project}
			\item {\bfseries{Technologies:} AWS, Terraform, Docker, Makefile, BASH, Python, maven, BitBucket pipelines, HTTPD}
		\end{cvitems}
	}
\end{cventrystack}
\end{minipage}

\cventry
{DevOps Engineer} % Job title
{Hubs - a Protolabs company} % Organization
{Amsterdam, Netherlands} % Location
{Jan 2020 - Mar 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Migrated a self-hosted RabbitMQ cluster into AmazonMQ with minimal downtime}
		\item {Proposed and developed the first Public ML pricing API as a hackathon project}
		\item {Implemented monitoring and alerting from the ground up with NewRelic}
		\item {Obsessed with NewRelic cost optimization: saving \$1300/month on average}
		\item {Migrated CI pipelines for Frontend and ML projects from Jenkins to Github Actions}
		\item {Performed Github Actions optimizations with parallelisation and smart caching}
		\item {Worked on the development of self-hosted kubernets on AWS - typhoon.psdn.io}
		\item {Cost optimizations for AWS by migrating, optimizing and automating resources}
		\item {Automated on/off-boarding into Github org.}
		\item {Interviewed people for Python engineer roles.}
		\item {\bfseries{Technologies:} AWS, Terraform, Docker, k8s, Github Actions, Python, Bash, Concourse}
	\end{cvitems}
}


\cventry{Senior Cloud Solution Engineer}
{Mirabeau - a Cognizant Digital Business}
{Amsterdam, Netherlands}
{Mar 2019 - Dec 2020}
{
	\begin{cvitems}
		\item {Worked with several clients, focusing on AWS, on-site and remotely}
		\item {Received the hero award of the year for technical writing - checkout my blog}
	\end{cvitems}
}

% Stack positions to show work for the same company.
\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
\xdef\tpd{\the\prevdepth}
\begin{cventrystack}
	\cventry
	{Senior Cloud Solution Engineer} % Job title
	{Karwei} % Organization
	{} % Location
	{Jul 2020 - Dec 2020} % Date(s)
	{
		\begin{cvitems}
			\item {Implementing requested functionality in Terraform on AWS}
			\item {Answering technical questions, related to AWS and CI/CD}
			\item {Participated in on-call rotation}
			\item {\bfseries{Technologies:} AWS, Terraform}
		\end{cvitems}
	}

	\cventry
	{Cloud Consultant} % Job title
	{Arcadia Group} % Organization
	{Remote} % Location
	{Jun 2020 - Jul 2020} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {POC for a client}
			\item {Migrated a legacy 3-tier POS system into AWS}
			\item {\bfseries{Technologies:} AWS, CloudEndure}
		\end{cvitems}
	}

	\cventry
	{Cloud Engineer} % Job title
	{Maxeda DIY Group} % Organization
	{} % Location
	{Mar 2019 - June 2020} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Worked with multiple dev and business teams}
			\item {Implemented CI/CD pipelines using Bitbucket pipelines}
			\item {Migrated monitoring and alerting from New relic into SignalFX, OpsGenie, Slack}
			\item {Migrated the self-hosted HTTP Apache edge servers into scalable microservices}
			\item {I was the goto person for the edge routing services}
			\item {Developed IaC for AWS in Ansible and Terraform}
			\item {Implemented various glue logic with Lambdas and Python}
			\item {\bfseries{Technologies:} AWS, Python, ECS, Docker, Terraform, SignalFX, Ansible, Apache, Logzio}
		\end{cvitems}
	}

\end{cventrystack}
\end{minipage}


\cventry
{DevOps Specialist} % Job title
{PVH Corp.} % Organization
{Amsterdam, Netherlands} % Location
{May 2018 - Feb. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
	\item {Reverse engineered proprietary Kong plugins}
	\item {Developed custom Kong plugins (complete with unit tests no questions asked) - check my github profile!}
	\item {Liaise with management and stakeholders (ISG, legal, directors) to migrate to AWS ASAP!}
	\item {Worked with a team to build centralised API hub fronting an IBM service}
	\item {\bfseries{Technologies:} VMWare, Lua, Docker, OVH cloud, WCS}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{DevOps developer} % Job title
{Vandebron Energie B.V.} % Organization
{Amsterdam, Netherlands} % Location
{Oct. 2017 - Feb. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {I built and deployed the infrastructure on Azure}
\item {Built a Kubernetes cluster to send massive amounts of emails cheaply with Scala.}
\item {Developed a bunch of CD/CI pipelines on Jenkins with Groovy}
\item {Automated services and infrastructure provisioning with Ansible and BASH}
\item {Developed several scripts for cleaning up stale resources on Kubernetes, Azure and GCP - cost saving}
\item {\bfseries{Technologies:} Azure, Kubernetes, Docker, Ansible, Nginx, NodeJS, Kafka, Scala }
\end{cvitems}
}

%------------------------------------------------

\cventry
{Conscript} % Job title
{Greek Army} % Organization
{Greece} % Location
{Mar. 2017 - Jun. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {It's a mandatory conscription, in case you were wondering about the career pause}
\item {\bfseries{Stack:} Wired telecommunications, G3A3 rifle}
\end{cvitems}
}

%------------------------------------------------

\cventry
{System administrator} % Job title
{Betiator gaming technologies} % Organization
{Athens, Greece} % Location
{Aug. 2015 - Oct. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Built and migrated from hosted to a microservice setup on bare metal before it was even a thing}
\item {Implemented a HA cluster based on Docker, Mesos, Marathon and Zookeeper.}
\item {Migrated to DC/OS.}
\item {Developed an automation framework for infrastructure autoscaling, recovery and reconfiguration.}
\item {Developed a soft shutdown and recovery program tied to physical UPS boxes.}
\item {Developed and scaled Couchbase cluster setups for storage.}
\item {Automated backups on physical tapes - Carefree backup system for my manager.}
\item {Built CI/CD pipelines with Groovy, Python and bash.}
\item {\bfseries{Technologies:} Docker, DC/OS, shell, Java, Wildfly, Redis, Node, Jenkins, Couchbase, Hadoop}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Linux administrator (intern)} % Job title
{IP Digital} % Organization
{Thessaloniki, Greece} % Location
{Oct. 2014 - Dec. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {I built a scalable virtualization platform on bare-metal blades.}
\item {Migrated later to Ovirt (bare metal cloud) and setup Proxmox to facilitate application hosting.}
\item {Implemented a backup NAS solution using Freenas and ZFS.}
\item {Developed automation scripts for provisioning and logging.}
\item {\bfseries{Technologies:} Ovirt, Unraid, Nas4free, Zfsguru, Nappit, Omnios, Openindiana, Nexenta, Proxmox}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Laboratory Assistant (Rewarding Scholarship)} % Job title
{Laboratory of Digital Systems and Computer Architecture} % Organization
{Kozani, Greece} % Location
{Mar. 2014 - Jun. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Supervised students on the courses}
\begin{itemize}
\item {Operating systems}
\item {Systems of parallel and distributed execution}
\item {Digital design}
\end{itemize}
\end{cvitems}
}

%------------------------------------------------

\cventry
{University Librarian (Rewarding Scholarship)} % Job title
{University Of Western Macedonia} % Organization
{Kozani, Greece} % Location
{Mar. 2013 - Jun. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {http://lib.uowm.gr/}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
